Precision calculations for cosmic shear

### 2017-02-08 limber2.tex
Some updates on the results section Purple text for MK to review
Added explicit links to the appendices in the intro

This paper is organised as follows.  In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.  In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.  We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.  This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.

@@

In this section we review the basic weak-lensing projection expressions, and
compute lensing power spectra for a spherical case, and in the flat-sky
approximation. Derivations for those expressions can be found in the appendix.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison of the approximations}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to CFHTLenS data}
\label{sec:cfhtlens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and comparison to previously published work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

This paper is organised as follows.  In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.  In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.  We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.  This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G, 2016arXiv161104954K}.   We present a discussion and comparison of our results to these papers in Appendix~\ref{app:B}.

@@

In this section we review the basic weak-lensing projection expressions, and
compute lensing power spectra for a spherical case, and in the flat-sky
approximation. For completeness we provide a derivations of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Comparison of the approximations}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application to CFHTLenS data}
\label{sec:cfhtlens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Conclusions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and comparison to previously published work}
\label{app:B}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
